Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-03-29 documents/cpm.tex
discussion

\section{Discussion}
We have presented a simple yet highly effective method that works in pixel-level 
based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ lightcurves, 
which is intended to search exoplanets. 
However, based on our assumption of the causal structure of the \Kepler\ 
data, if we turn off the auto-regressive components and keep the predictors from other
stars working  in the \name, we should be able to still remove the systematics while
preserve the intrinsic stellar  variability, since there is no reason that these independent
stars can be used to predict the stellar variability of the target star. However, in fact, we
can not preserve the stellar variability just by turning off the auto-regressive 
components. One possible reason can be that, since our model is so flexible 
(thousands of parameters), in principle it can fit any functions. In this sense, we should 
run cross-validation with the auto-regressive components turned off and to find out how
many pixels from other stars we need to just remove systematics while preserve stellar
variability, but in fact we do not have a good criterion to check how well we preserve
stellar variability in cross-validation because we do not have enough knowledge of the 
true stellar variability. Thus for the time being, we just focus on producing well-
calibrated light curves for searching exoplanets, but in long term, we are looking
forward to find a method to preserve the stellar variability.

>>>>

\section{Discussion}
We have presented a simple yet highly effective method---the \name\ that works in pixel-level 
  based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ lightcurves, 
  which is intended to search exoplanets.
In \name, systematics and stellar variabilities are removed by% 
  either fitting with other stars' lightcures or auto-regressive components,
  while transit signals can still be perfectly preserved by train-and-test framework.
Low variable clean lightcurves can be produced by \name\,  which is ideal for transit planet searching. 
The CDPP noise level estimation is also presented in the paper to show the performance of \name.

\todo{Compare with PDC, median filter, pre-whitening}

However, based on our assumption of the causal structure of the \Kepler\ data, 
  if we turn off the auto-regressive components and keep the predictors from other stars working in the \name, 
  we should be able to still remove the systematics while preserve the intrinsic stellar variability, 
  since there is no reason that these independent stars can be used to predict the stellar variability of the target star.
However, in fact, we can not preserve the stellar variability just by turning off the auto-regressive components. 
One possible reason can be that, since our model is so flexible (thousands of parameters), 
  in principle it can fit any functions. 
In this sense, 
  we should run cross-validation with the auto-regressive components turned off 
  and to find out how many pixels from other stars we need to just remove systematics 
  while preserve stellar variability, 
  but in fact we do not have a good criterion to check how well we preserve stellar variability in cross-validation 
  because we do not have enough knowledge of the true stellar variability. 
Thus for the time being, we just focus on producing well-calibrated light curves for searching exoplanets, 
  but in long term, we are looking forward to find a method to preserve the stellar variability.

Another issue of the \name\ is that when there are strong transit signals in the lightcurve,  
  one can find distortion around the these signals.
We think this problem is caused by the train-and-test framework.
Train-and-test framework is applied in the \name\ to preserve the transit signals, 
  in which data points in a certain excluded window are separated from the model.
However, for data points half-window size away from the transit signals, 
  the prediction of these points in \name\ is largely influenced by the strong transit signal.
That is,  these points are predicted to be a little bit smaller than they should be, 
  since transit signal (negative points away from the continuum) makes the model think
  there is a decreasing trend in this region.
This window edge effect is a trade-off of the train-and-test framework that is crucial for \name,
 and can not be solved in the scope of \name.
